MSAD_PCA_Walkthrough

### 2017-11-03 README.Rmd
Added CRAN tags to the README file. I'm leaving the Travis-CI tag for the development version of the package. Closes #26.

[![Travis-CI Build Status](https://travis-ci.com/gabrielodom/mvMonitoring.svg?token=ZzKTz9X2qQxWeqCPkaKq&branch=master)](https://travis-ci.com/gabrielodom/mvMonitoring)

>>>>

Travis Status (Devel v. 0.1.1) and CRAN Status (Stable v. 0.1.0)

[![Travis-CI Build Status](https://travis-ci.com/gabrielodom/mvMonitoring.svg?token=ZzKTz9X2qQxWeqCPkaKq&branch=master)](https://travis-ci.com/gabrielodom/mvMonitoring)
![CRAN Build Status](http://www.r-pkg.org/badges/version/mvMonitoring)
